### 2020-10-05 paper/revisions/review-responses.tex

        \question  The total demands of different control rods systems should be discussed first. According to the demands of nuclear safety regulations, two different shutdown systems of SSD and CSD must be adopted in a reactor design to ensure the reactor safe operation, to adjust power and to ensure the shutdown of reactor etc. All the shutdown systems must meet the shutdown margin of the reactor. For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods etc. Hence, the sizes of different control rods should be further optimized to realize their functional properties.
        \begin{solution}

        		Thank you for the excellent point. The demands of different control rods systems have been discussed in the manuscript. Optimization of different control rods sizes will be done in our future work.

        		The following paragraph has been added to the manuscript to clarify this point:\\

The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects the reactor safety \cite{atkinson2019small}. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}. According to the demands of nuclear safety regulations, two independent shutdown systems must ensure the reactor safe operation, adjust power, and ensure the shutdown of the reactor anytime independently. All the shutdown systems must be sufficient to shut down the reactor at any time during operation.

@@

        \end{solution}

        %---------------------------------------------------------------------
        \question  Although Xe can be online removed during regular operation, it may remain in the core in the event of the bubble system failure. Hence, the Xenon poison effect of the SD-TMSR should be assessed for the designs of SSD and CSD. 
        \begin{solution}

		         Thank you for the excellent point. The xenon poison effect is not considered in this paper, but we intend to study this phenomenon in our upcoming article when calculating the worth of the control rods during fuel depletion. The present work focuses on the steady-state calculations without taking into account fuel salt depletion.

@@

		         The following sentence has been added to the future work to clarify this point:\\

		         The xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.

@@

     The assessment of the optimal absorber radius should be an essential consideration. If the CR radius is too large, the absorber material is not effectively utilized due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~2 illustrates the change of the $k_{eff}$ with the radius of the control rod for all different materials. As shown in Figure~2, in the region between 0.0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius for all absorbers. However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have a relatively low chance for neutron capture. In contrast, other absorbers are not affected by the self-shielding phenomenon in the considered region (0.0$<$r$<$1.0 cm). From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).

\end{solution}
%---------------------------------------------------------------------

\question As shown in Figure~3, only a small thickness of gap of 0.1 cm is designed in a control rod, which would not meet the heat release requirements. It is necessary to evaluate the thermal emission behavior of the control rods, since the control rod material would release a large amount of heat after absorbing neutrons.
\begin{solution}

    Thank you for the suggestion. Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}. We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.

@@

	The following paragraph has been added to the text to clarify this point:\\

	Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}. We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.

@@

\end{solution}
%---------------------------------------------------------------------

\question Table~3 lists the initial excess reactivity for different fissile fuel component. Please clarify the corresponding actual reactivity of 1 \$ for each fissile fuel, since all of them may be significantly different from each other. In addition, why is the initial excess reactivity of TRU fuel significantly higher than that of 233U? Also, the large initial excess reactivity of TRU fuel may affect the total SDMs of the different control rods in Table 6.
\begin{solution}

	Thank you for the questions. Now all initial excess reactivities are listed in Table~5 in [pcm] unit. Regarding the initial excess reactivity of TRU fuel; The TRU composition includes substantial thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly. Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}. The proposed reactivity control system must compensate such reactivity at startup and during burnup.

@@

	The following sentence has been added to the conclusion to clarify this point:\\

	The TRU composition includes substantial thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly. Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}. The proposed reactivity control system must compensate such reactivity at startup and during burnup.

@@

The integral CRWs are calculated for three different systems: all CRs, CSD, and SSD systems. We calculated the differential CRWs for the CSD system only because special adjusting rods (i.e., CSD) were assumed to adjust the reactivity.

\end{solution}
%---------------------------------------------------------------------

\question Please assess whether the control rods would still meet the shutdown requirement if a single control rod with maximum worth is withdrawn.
\begin{solution}

	Thank you for your suggestion. Table~10 lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn. As shown in Table~10 the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu. For the TRU case, in the case of SSD1 cluster failure, substitutional insertion of CSD with SSD clusters will provide a sufficient positive SDM.

@@

		The following paragraph has been added to the manuscript to clarify this point:\\

	Table~10 lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn. As shown in Table~10 the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu. For the TRU case, in the case of SSD1 cluster failure, substitutional insertion of CSD with SSD clusters will provide a sufficient positive SDM.

@@

              Thank you for the comment. The statement has been removed from the text.

        \end{solution}

        %--------------------------------------------------------------------
        \question How is 0.1 cm a reasonable gap between the cladding and guide tube?
        \begin{solution}

Thank you for the question. Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}. We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.

@@

Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}. We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.

        \end{solution}

        %--------------------------------------------------------------------
        \question Why do the four rods break the 60-degree symmetry of the fuel assemblies?

        \begin{solution}
                 Thank you for the excellent point. We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element. The SD-TMSR initially loaded by TRU was selected for this analysis due to the maximum excess reactivity at startup. As shown in Figure~8, the three rods in the graphite element save the 60-degree symmetry of the component; however, results show that the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$. In the case of four rods, the 60-degree symmetry of the graphite element is broken; however, the SDM is about $228$ $pcm$, and the A$_{CRi}$ is $0.97$. Finally, when six rods are distributed evenly in the graphite element, both symmetry and relatively high SDM are obtained ($598$ $pcm$), but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case. Therefore the 3- and 6-CRs configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively. The 4-CRs configuration is adopted in the current study since the SDM is positive, and almost no shadowing effect has been observed.

@@

                 The following paragraph has been added to the manuscript:\\

We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element. The SD-TMSR initially loaded by TRU was selected for this analysis due to the maximum excess reactivity at startup. As shown in Figure~8, the three rods in the graphite element save the 60-degree symmetry of the component; however, results show that the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$. In the case of four rods, the 60-degree symmetry of the graphite element is broken; however, the SDM is about $228$ $pcm$, and the A$_{CRi}$ is $0.97$. Finally, when six rods are distributed evenly in the graphite element, both symmetry and relatively high SDM are obtained ($598$ $pcm$), but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case. Therefore the 3- and 6-CR configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively. The 4-CRs configuration is adopted in the current study since the SDM is positive, and almost no shadowing effect has been observed.

@@

 %--------------------------------------------------------------------
\question Please speak more to the anti-shadowing effects observed for CSD9 and SSD4.
\begin{solution}
	Thank you for your suggestion.

	The following paragraphs have been added to the manuscript:\\

	As listed in Tables~6 and ~7, the strongest anti-shadowing effect occurred in 
	SSD4 and CSD9 clusters that are located at the boundary between the core zones 
	with different moderator-to-fuel ratios. This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~5). Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).

\end{solution}
 %--------------------------------------------------------------------
\question What is "sufficient positive SDM"? This phrase is unspecific. What is sufficient? Be more specific here.
\begin{solution}
	Thank you for your question. We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total fraction of delayed neutron precursors. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.

@@

	The following phrase has been added to the manuscript:\\

	We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total fraction of delayed neutron precursors. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.

### 2020-10-05 paper/conclusion.tex
minor edits from Prof. Huff

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case). Increasing the number of SSD clusters would provide a sufficient positive SDM for the TRU case.

@@

\section{Future work}
The authors intend to evaluate the effect of the fuel salt 
depletion on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018}. 
The Xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.
Additionally, the authors intend to investigate
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

>>>>

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case). For the TRU case, in the case of SSD1 cluster failure, substitutional insertion of CSD with SSD clusters will provide a sufficient positive SDM.

@@

\section{Future work}
The authors intend to evaluate the effect of the fuel salt 
depletion on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018}. 
The xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.
Additionally, the authors intend to investigate
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

### 2020-10-05 paper/methods.tex
minor edits from Prof. Huff

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\ 
		Fuel volume, m$^3$  &	52.9 \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Graphite density, g/cm$^3$             	    & 2.3	\\ 
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Upper plenum, cm								& 30  \\
		Lower plenum, cm								& 30  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Radius (inner fuel channel), cm							& 3.5  \\
		Radius (outer fuel channel), cm							& 5  \\
		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\

@@

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{Radius.png}
	\caption{The change of the effective multiplication factor with the radius of the B$_4$C control rod.}
	\label{fig:Radius}
\end{figure}

The assessment of the optimal absorber radius should be an essential consideration. If the CR radius is too large, the absorber material is not effectively utilized due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the control rod for all different materials. As shown in Figure~\ref{fig:Radius}, in the region between 0.0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius for all absorbers. However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have a relatively low chance for neutron capture. In contrast, other absorbers are not affected by the self-shielding phenomenon in the considered region (0.0$<$r$<$1.0 cm). From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}. We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work. All densities of rod materials are listed in
Table~\ref{tab:table111}.

>>>>

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020thermal}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\ 
		Fuel volume, m$^3$  &	52.9 \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Graphite density, g/cm$^3$             	    & 2.3	\\ 
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Upper plenum, cm								& 30  \\
		Lower plenum, cm								& 30  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Radius (inner fuel channel), cm							& 3.5  \\
		Radius (outer fuel channel), cm							& 5  \\
		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\

@@

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{Radius.png}
	\caption{The change of the effective multiplication factor with the radius of the control rod for all different absorbers.}
	\label{fig:Radius}
\end{figure}

The assessment of the optimal absorber radius should be an essential consideration. If the CR radius is too large, the absorber material is not effectively utilized due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the control rod for all different materials. As shown in Figure~\ref{fig:Radius}, in the region between 0.0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius for all absorbers. However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have a relatively low chance for neutron capture. In contrast, other absorbers are not affected by the self-shielding phenomenon in the considered region (0.0$<$r$<$1.0 cm). From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}. We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work. All densities of rod materials are listed in
Table~\ref{tab:table111}.
